### 2016-02-09 prepReport/stateArt.tex
Only the overview is missing on the State of the Art chapter

\begin{itemize}
    \item \textbf{Handwriting Recognition} -- and LSTM-based network~\cite{Bertolami09}, submitted by a team of the Technische Universität München, won the 2009 ICDAR Handwriting Recognition Contest, achieveing a recognition rate of up to 91\%~\cite{ICDAR09}.
    \item \textbf{Speech Recognition} -- an architecture\cite{Graves13} proposed by Graves et al. in 2013 achieved an astonishing 17.7\% of accuracy on the TIMT Phoneme Recognition Benchmark, which up to the date is a new record. Furthermore, it has also been used for large scale acoustic modelling of speech~\cite{Sak14}.
    \item \textbf{Handwriting Synthesis} -- 
    \item \textbf{Speech Synthesis} --
    \item \textbf{Translation} -- LSTM was used by Sutskever et al. (Google) to perform sequence-to-sequence translation on the WMT'14 dataset, translating English to French with a close to state of the art score~\cite{Sustkever14}.

@@

    \item \textbf{Video and Image Analysis} --

>>>>

\begin{itemize}
    \item \textbf{Handwriting Recognition} -- and LSTM-based network~\cite{Bertolami09}, submitted by a team of the Technische Universität München, won the 2009 ICDAR Handwriting Recognition Contest, achieveing a recognition rate of up to 91\%~\cite{ICDAR09}. LSTMs have also proven to surpass HMM based models in terms of optical character recognition in printed text, as~\cite{Breuel13} suggests.

    \item \textbf{Speech Recognition} -- an architecture\cite{Graves13} proposed by Graves et al. in 2013 achieved an astonishing 17.7\% of accuracy on the TIMT Phoneme Recognition Benchmark, which up to the date is a new record. Furthermore, it has also been used for large scale acoustic modelling of speech~\cite{Sak14}.

    \item \textbf{Handwriting Synthesis} -- a comprehensive study by Graves shows, among other sequence generation tasks such as Text Prediction, the use of LSTM to produce synthetic handwriting, that looks incredibly similar to human-produced handwriting~\cite{Graves13_2}.

    \item \textbf{Translation} -- LSTM was used by Sutskever et al. (Google) to perform sequence-to-sequence translation on the WMT'14 dataset, translating English to French with a close to state of the art score~\cite{Sustkever14}.

@@

    \item \textbf{Video and Image Analysis} -- Vinyals et al., at Google, proposed and LSTM network for \textbf{image captioning}, preceded by a Convolutional Neural Network to apply preprocessing to the images~\cite{Vinyals14}. This way, the LSTM works as \emph{sentence generator}, that captions the images, with state of the art performance. 
        Besides image captioning, video captioning is also an interesting topic. Venugopalan et al. recently proposed a CNN + LSTM architecture to translate video sequences to natural language~\cite{Donahue14}, using the Microsoft Research Video Description Corpus as a dataset.Tthere are other similar studies that combine image and video captioning~\cite{Donahue14_2}.
